---
title: "Megahand_Presentation"
author: "Joe"
date: "12/6/2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

Package load and Install
```{r}
# install.packages("tidyverse")
# install.packages("tensorflow", dependencies = TRUE)
# install.packages("keras", dependencies = TRUE)
# install.packages("reticulate", dependencies = TRUE)

library(tidyverse)
library(reticulate)
library(keras)
```

```{python}
# Library import
import numpy as np
import pandas as pd
import matplotlib.pyplot as plt
import rpytools as rpy
```

## Slide with R Output
```{r}
source_python("TrainingDataGrabber.py")
as.data.frame(Training_Data_Files)
```

## Slide with Plot

